\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-14 k-planar.tex
Pfffff

To see that $H$ is planar, imagine adding a vertex consider a plane multigraph $G''$ obtained by adding a vertex $v_\tau$ in the interior of some of the faces of $G'$.  When creating a new part $S:=V(\tau\cup Q_1\cup Q_2\cup Q_3-F)$ of $\mathcal{P}$, add a vertex $v_\tau$ to the interior of $\tau$ that is adjacent to each vertex of $\tau$.  The graph $G''\supseteq G'$ obtained this way is clearly planar.  Furthermore, for each part $P\in\mathcal{P}$, $G''[P]$ is connected.  Since planarity is preserved under edge contraction, it follows that $G''/\mathcal{P}$ is planar.  Now argue that $G/\mathcal{P}=G''/\mathcal{P}$.
}

>>>>

To see that $H$ is planar, consider a plane multigraph $G''$ obtained by adding stars in some of the faces of $G'$, as follows:  When creating the part $S$, add a vertex $v_\tau$ to the interior of $\tau$ that is adjacent to each vertex of $\tau$ and place $v_\tau$ in $S$.  The graph $G''\supseteq G'$ obtained this way is clearly planar.  Furthermore, for each part $P\in\mathcal{P}$, $G''[P]$ is connected.  Since planarity is preserved under edge contraction, it follows that $G''/\mathcal{P}$ is planar.  Now argue that $G/\mathcal{P}=G''/\mathcal{P}$\ldots
}
